\papertitle

### 2021-03-10 source_separation/paper/paper.tex
fix typo in affiliations

%%Affiliations
\affil[1]{\department{Center for New Music and Audio Technologies}\institution{University of California, Berkeley}\city{Berkeley}\state{California}\country{USA}\affiliationtype{University}}
\affil[2]{\department{\'Ecole Normale Sup\'erieure Paris-Saclay}\institution{Universi\'e Paris-Saclay}\city{Paris}\state{}\country{France}\affiliationtype{University}}
\affil[3]{\department{Laboratoire des Signaux et Syst\`emes}\institution{Centrale Sup\'elec, CNRS, Universit\'e Paris-Saclay}\city{Paris}\state{}\country{France}\affiliationtype{University}}

>>>>

%%Affiliations
\affil[1]{\department{Center for New Music and Audio Technologies}\institution{University of California, Berkeley}\city{Berkeley}\state{California}\country{USA}\affiliationtype{University}}
\affil[2]{\department{\'Ecole Normale Sup\'erieure Paris-Saclay}\institution{Universit\'e Paris-Saclay}\city{Paris}\state{}\country{France}\affiliationtype{University}}
\affil[3]{\department{Laboratoire des Signaux et Syst\`emes}\institution{Centrale Sup\'elec, CNRS, Universit\'e Paris-Saclay}\city{Paris}\state{}\country{France}\affiliationtype{University}}
